High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-26 notebooks/mnist.qmd
attempting a run without normalising digits to between -1 and 1

```{julia}
function pre_process(x; noise::Float32=0.03f0)
    ϵ = Float32.(randn(size(x)) * noise)
    x = @.(2 * x - 1) .+ ϵ
    return x
end
```

```{julia}
# Hyper:
_retrain = false
_regen = false

@@

```{julia}
# JEM parameters:
𝒟x = Uniform(-1,1)
𝒟y = Categorical(ones(output_dim) ./ output_dim)
sampler = ConditionalSampler(
    𝒟x, 𝒟y, 
    input_size=(input_dim,), 
    batch_size=10,
)
α = [1.0,1.0,1e-2]      # penalty strengths
```

@@

measure = Dict(
    :f1score => multiclass_f1score, 
    :acc => accuracy, 
    :precision => multiclass_precision
)
model_performance = DataFrame()
for (mod_name, mod) in model_dict
    # Test performance:
    test_data = load_mnist_test()
    test_data.X = pre_process.(test_data.X, noise=0.0f0)
    _perf = CounterfactualExplanations.Models.model_evaluation(mod, test_data, measure=collect(values(measure)))
    _perf = DataFrame([[p] for p in _perf], collect(keys(measure)))
    _perf.mod_name .= mod_name
    model_performance = vcat(model_performance, _perf)
end
Serialization.serialize(joinpath(output_path,"mnist_model_performance.jls"), model_performance)
CSV.write(joinpath(output_path, "mnist_model_performance.csv"), model_performance)
model_performance
```

>>>>

```{julia}
function pre_process(x; noise::Float32=0.03f0)
    ϵ = Float32.(randn(size(x)) * noise)
    # x = @.(2 * x - 1) 
    x += ϵ
    return x
end
```

```{julia}
# Hyper:
_retrain = true
_regen = true

@@

```{julia}
# JEM parameters:
𝒟x = Uniform(0,1)
𝒟y = Categorical(ones(output_dim) ./ output_dim)
sampler = ConditionalSampler(
    𝒟x, 𝒟y, 
    input_size=(input_dim,), 
    batch_size=10,
)
α = [1.0,1.0,1e-2]      # penalty strengths
```

@@

measure = Dict(
    :f1score => multiclass_f1score, 
    :acc => accuracy, 
    :precision => multiclass_precision
)
model_performance = DataFrame()
for (mod_name, mod) in model_dict
    # Test performance:
    test_data = load_mnist_test()
    # test_data.X = pre_process.(test_data.X, noise=0.0f0)
    _perf = CounterfactualExplanations.Models.model_evaluation(mod, test_data, measure=collect(values(measure)))
    _perf = DataFrame([[p] for p in _perf], collect(keys(measure)))
    _perf.mod_name .= mod_name
    model_performance = vcat(model_performance, _perf)
end
Serialization.serialize(joinpath(output_path,"mnist_model_performance.jls"), model_performance)
CSV.write(joinpath(output_path, "mnist_model_performance.csv"), model_performance)
model_performance
```
